New insights into the Weddell Sea ecosystem applying a network approach

### 2022-11-07 Manuscript/Manuscript.Rmd
Finished Results

Finally, we run extinction simulations and estimated its impact on the stability of the network. For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008]. If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016].

@@

Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat. With this we aim to characterize those species with a relatively higher effect on the stability of the food web.

@@

Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties (Figure 4), we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength. We also found a positive relationship with the degree (total number of interactions). On the other hand, there was no evident relationship with trophic similarity. Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" concentrated the majority of the species with relatively higher interaction strength. Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).

CONTINUE MODIFYING HERE:
The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties. It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A). On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships comparing groups. These mean that in species with relatively higher mean interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B). Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).

@@

It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index. Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling p-value > 0.01, see Supplementary Material). This is shown in Figure 5 A-D, where most of the points lie around the zero value of the 'Stability difference' y axis. This means that the stability for the food web minus a given species is similar to the stability for the whole network. However, there were few species that when become extinct altered significantly the stability (QSS) of the food web. Most of such species generated positive significant differences in the stability of the food web, meaning that they increased the network's stability when deleted. There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability. Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the network's stability.

NEED TO BE CHANGED
When plotting the stability difference against species properties and the previous results regarding clustering, interesting insights arose (Figure 6). In the first place, all species with a significant impact on the stability belong to the 'High IS' group, denoting a high mean interaction strength (Figure 6A). Secondly, these species are positioned in high trophic levels (TL > 3.7) (Figure 6B). Thirdly, they have a relatively high number of interactions or degree (Degree > 25) (Figure 6C). Regarding trophic similarity, species have mid to low values (TS < 0.13) (Figure 6D). Habitat wise, species live in all the habitats, except for are benthic (Figure 6E). Table 2 shows these results per species.

@@

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
knitr::include_graphics("Fig4_LinReg.png")
```

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat. Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
knitr::include_graphics("Fig.5_QSSDif.png")
```

@@

```{=tex}
\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p value). All species belong to the 'High IS' group.  References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p value.}
\begin{tabular}{l c c c c c c c}
\tophline

>>>>

Finally, we run extinction simulations and estimated its impact on the stability of the food web. For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008]. If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016].

@@

Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat. With this we aim to characterize those species with a relatively high effect on the stability of the food web.

@@

Regarding the species' mean interaction strength and its relationship with the unweighted properties (Figure 4A-D), we found that interaction strength-trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength. We also found a significant but less evident positive relationship with degree (total number of interactions). On the other hand, there was no significant relationship with trophic similarity. Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength. Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).

@@

It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index. Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5). This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar to the stability for the whole network. However, there were few species that when become extinct altered significantly the stability (QSS) of the food web. Most of such species generated positive significant differences in the stability of the food web, which mean that they increased the network's stability when deleted. There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability. Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the food web's stability (Table 2).

After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web are characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity values (TS < 0.16). Habitat wise, species with a significant impact on the stability are in all habitats, except for the benthic realm. Table 2 shows the results for such species.

@@

Dominance of weak interactions in concordance with other studies.

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
knitr::include_graphics("Fig4_LinReg.png")
```

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat. Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
knitr::include_graphics("Fig.5_QSSDif.png")
```

@@

```{=tex}
\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value). References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
\begin{tabular}{l c c c c c c c}
\tophline

### 2022-11-07 Manuscript/Manuscript.tex
Finished Results

This marine food web compiles all the food web data available for the
high Antarctic Weddell Sea collected since 1983, and is one of the most
highly-resolved marine food webs documented to date. It's noteworthy
that it is a summary network that ignores seasonal changes
\citep{Jacob2011}.

@@

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are: body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality classified as 2 or 3
dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and
resources (except for `detritus' and `sediment') and the dimensionality
for every interaction, though the latter is missing for 924
interactions. To solve this issue, we used information about movement
type for consumer and resource included in GATEWAy. Then, we classified
the interaction as 2D if both consumer and resource move in 2D (e.g.,
both are sessile or walking) or if a consumer moves in 3D and a resource
in 2D (e.g., swimming consumer and sessile/walking resource). The
interaction was classified as 3D if both consumer and resource move in
3D (e.g., both swimming) or if the consumer moves in 2D and the resource
in 3D (e.g., sessile/walking consumer, swimming resource)
\citep{Pawar2012}.

@@

We obtained estimations for the resource density and the search rate
from the scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On one hand, resource density scales with
resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in
2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
`phytodetritus' and `sediment' were not available in GATEWAy, we
considered the body mass of the smallest phytoplankton species
(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
that `phytodetritus' and `sediment' are mainly composed by dead or
senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
the other hand, search rate scales with consumer mass as a power-law
with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08}
in 3D.

After this, we fit the interaction strength distribution of the food web
considering six candidate models (Exponential, Gamma, log-Normal,
Normal, Power-law and Uniform) using maximum likelihood
\citep{McCallum2008}, and selected the model performance by computing
the Akaike Information Criterion AIC \citep{Burnham2002}.

@@

In order to individually characterize the species of the food web, we
considered weighted and unweighted properties (Figure 2). The former is
based on the estimation of the interaction strength described in the
previous section. The latter is related to properties commonly used in
qualitative (presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}.

As the weighted property we took into account the mean interaction
strength, meaning the average strength of all species' interactions. On
the other hand, we considered the following unweighted properties: a)
degree or the total number of trophic interactions, taking into account
in- and out-coming interactions (role as predator and prey,
respectively); b) trophic level or the position in the food web relative
to primary producers/detritus; and c) trophic similarity or the trophic
overlap between species based on shared and unique resources and
consumers. The following are arguments to have selected the above
properties. The degree has often been equated with importance to the
structure and functioning of a community, i.e.~perturbations to
high-degree species may therefore have larger effects on the food web
than perturbations to low-degree species
\citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e.~top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. The trophic
similarity measures the similarity of one of the most important aspect
of species' niches, the trophic niche, and functional aspects of
biodiversity \citep{Martinez1991, Williams2000}.

Furthermore, we took into account the species' habitat, which describes
the physical position of a species within the environment. These data
was taken from \citet{Jacob2011}. Species were categorized as: 1)
benthic, if the species lives on the seafloor; 2) pelagic, if the
species lives close to the surface; 3) benthopelagic, if it moves
between and connects the mentioned environments; 4) demersal, if it
lives and feeds on or near the bottom of the sea; and 5) land-based, if
the consumer is not aquatic but feeds predominantly in the marine realm.

With the aim of studying the relationship between the interaction
strength of the species and its unweighted properties and habitat, we
performed linear regression analyses between the log(mean interaction
strength) and each of the mentioned unweighted properties.

@@

Finally, we run extinction simulations and estimated its impact on the
stability of the network. For this, we calculated a stability index
called Quasi-Sign Stability (QSS), which is the proportion of stable
networks using randomized Jacobians and keeping the predator-prey sign
structure fixed \citep{Allesina2008}. If this proportion is zero, then
one should take into account the real part of the maximum eigenvalue of
the Jacobian matrix, which is also a measure of stability
\citep{Grilli2016}.

@@

Regarding the distribution of the species' mean interaction strength and
its relationship with the unweighted properties (Figure 4), we found
that interaction strength-trophic level showed the strongest linear
regression: the higher the trophic level of the species, the higher its
mean interaction strength. We also found a positive relationship with
the degree (total number of interactions). On the other hand, there was
no evident relationship with trophic similarity. Considering species
habitat, the ``Benthopelagic'' and ``Pelagic'' categories presented the
two species with the highest mean interaction strength, though
``Demersal'' and ``Land-based'' concentrated the majority of the species
with relatively higher interaction strength. Species inhabiting the
benthic realm showed the lowest mean interaction strength (Figure 4D).

CONTINUE MODIFYING HERE: The so-called `High IS' and `Low IS' groups of
species exhibited different and, in some cases, opposite relationships
with unweighted properties. It's noteworthy that only the relationship
with trophic level revealed a similar trend in the regression analysis
for both groups: mean interaction strength increases with trophic level
(Figure 5A). On the contrary, the linear regressions with degree and
trophic similarity showed opposite relationships comparing groups. These
mean that in species with relatively higher mean interaction strength,
`High IS', such strength decreases when the number of interactions
(degree) increases; the opposite occurs in species with relatively lower
interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,
the interaction strength decreases in `High IS' species while increases
in `Low IS' species (Figure 5C).

@@

It's important to note that since the proportion of Jacobians that are
locally stable or QSS was zero for the Weddell Sea food web, we
considered the mean maximum eigenvalue as the stability index. Our
results showed that the majority of the species had no significant
impact on the stability of the food web when extinct (Anderson-Darling
p-value \textgreater{} 0.01, see Supplementary Material). This is shown
in Figure 5 A-D, where most of the points lie around the zero value of
the `Stability difference' y axis. This means that the stability for the
food web minus a given species is similar to the stability for the whole
network. However, there were few species that when become extinct
altered significantly the stability (QSS) of the food web. Most of such
species generated positive significant differences in the stability of
the food web, meaning that they increased the network's stability when
deleted. There were two exceptions, Pagetopsis macropterus (demersal
fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when
deleted decreased the stability. Overall, 15 out of 490 species (3.06\%)
gave rise to significant changes in the network's stability.

NEED TO BE CHANGED When plotting the stability difference against
species properties and the previous results regarding clustering,
interesting insights arose (Figure 6). In the first place, all species
with a significant impact on the stability belong to the `High IS'
group, denoting a high mean interaction strength (Figure 6A). Secondly,
these species are positioned in high trophic levels (TL \textgreater{}
3.7) (Figure 6B). Thirdly, they have a relatively high number of
interactions or degree (Degree \textgreater{} 25) (Figure 6C). Regarding
trophic similarity, species have mid to low values (TS \textless{} 0.13)
(Figure 6D). Habitat wise, species live in all the habitats, except for
are benthic (Figure 6E). Table 2 shows these results per species.

@@

\begin{figure}
\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat. Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p value). All species belong to the 'High IS' group.  References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p value.}
\begin{tabular}{l c c c c c c c}
\tophline

>>>>

This marine food web compiles all the trophic data available for the
high Antarctic Weddell Sea collected since 1983, and is one of the most
highly-resolved marine food webs documented to date. It's noteworthy
that it is a summary network that ignores seasonal changes
\citep{Jacob2011}.

@@

To estimate the strength of each interaction in the food web we followed
the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are: body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality classified as 2 or 3
dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and
resources (except for `detritus' and `sediment') and the dimensionality
for the majority of the interactions, though the latter is missing in
some cases (924 interactions). To complete such missing data, we used
information about movement type for consumer and resource included in
GATEWAy. Thus, we classified the interaction as 2D if both consumer and
resource move in 2D (e.g., both are sessile or walking) or if a consumer
moves in 3D and a resource in 2D (e.g., swimming consumer and
sessile/walking resource). The interaction was classified as 3D if both
consumer and resource move in 3D (e.g., both swimming) or if the
consumer moves in 2D and the resource in 3D (e.g., sessile/walking
consumer, swimming resource) \citep{Pawar2012}.

@@

We obtained estimations for the resource density and the search rate
from the scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On one hand, resource density scales with
resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D
and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
`phytodetritus' and `sediment' were not available in GATEWAy, we
considered the body mass of the smallest phytoplankton species
(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
that `phytodetritus' and `sediment' are mainly composed by dead or
senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
the other hand, search rate scales with consumer mass as power-law with
exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in
3D.

Finally, we fit the interaction strength distribution of the food web
considering six candidate models (Exponential, Gamma, log-Normal,
Normal, Power-law and Uniform) using maximum likelihood
\citep{McCallum2008}, and selected the model performance by computing
the Akaike Information Criterion AIC \citep{Burnham2002}.

@@

In order to individually characterize the species of the food web, we
considered weighted and unweighted properties (Figure 2). The former is
based on the estimation of the interaction strength described in the
previous section. The latter is related to properties commonly used in
qualitative or topological (presence/absence of interaction) food web
studies \citep{Martinez1991, Dunne2002, Borrelli2014}.

As the weighted property we took into account the total mean interaction
strength, meaning the average strength of all species' interactions for
each species. On the other hand, we considered the following unweighted
properties: a) degree or the total number of trophic interactions,
summing up in- and out-coming interactions (role as predator and prey,
respectively); b) trophic level or the position in the food web relative
to primary producers/detritus; and c) trophic similarity or the trophic
overlap based on shared and unique resources and consumers. The
following are arguments to have selected the unweighted properties. The
degree has often been equated with importance to the structure and
functioning of a community, i.e.~perturbations to high-degree species
may therefore have larger effects on the food web than perturbations to
low-degree species \citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e.~top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. The trophic
similarity measures one of the most important aspects of species'
niches, the trophic niche, and functional aspects of biodiversity
\citep{Martinez1991, Williams2000}.

Furthermore, we took into account the species' habitat, which describes
the physical position of a species within the ecosystem. Species were
categorized as: 1) benthic, if the species lives on the seafloor; 2)
pelagic, if the species lives close to the surface; 3) benthopelagic, if
it moves between and connects the mentioned environments; 4) demersal,
if it lives and feeds on or near the bottom of the sea; and 5)
land-based, if the consumer is not aquatic but feeds predominantly in
the marine realm. These data was taken from \citet{Jacob2011}.

With the aim of studying the relationship between the interaction
strength of the species (weighted property) and its unweighted
properties we performed linear regression analyses between the log(mean
interaction strength) and each of the mentioned unweighted properties.
We also explored such weighted property with species habitat.

@@

Finally, we run extinction simulations and estimated its impact on the
stability of the food web. For this, we calculated a stability index
called Quasi-Sign Stability (QSS), which is the proportion of stable
networks using randomized Jacobians and keeping the predator-prey sign
structure fixed \citep{Allesina2008}. If this proportion is zero, then
one should take into account the real part of the maximum eigenvalue of
the Jacobian matrix, which is also a measure of stability
\citep{Grilli2016}.

@@

Regarding the species' mean interaction strength and its relationship
with the unweighted properties (Figure 4A-D), we found that interaction
strength-trophic level showed a significant positive linear regression:
the higher the trophic level of the species, the higher its mean
interaction strength. We also found a significant but less evident
positive relationship with degree (total number of interactions). On the
other hand, there was no significant relationship with trophic
similarity. Considering species habitat, the ``Benthopelagic'' and
``Pelagic'' categories presented the two species with the highest mean
interaction strength, though ``Demersal'' and ``Land-based'' habitats
concentrated the majority of the species with relatively higher
interaction strength. Species inhabiting the benthic realm showed the
lowest mean interaction strength (Figure 4D).

@@

It's important to note that since the proportion of Jacobians that are
locally stable or QSS was zero for the Weddell Sea food web, we
considered the mean maximum eigenvalue as the stability index. Our
results showed that the majority of the species had no significant
impact on the stability of the food web when extinct (Figure 5). This is
shown in Figure 5, where most of the points lie around the zero value of
the `Stability difference' y axis, meaning that the stability for the
food web minus a given species is similar to the stability for the whole
network. However, there were few species that when become extinct
altered significantly the stability (QSS) of the food web. Most of such
species generated positive significant differences in the stability of
the food web, which mean that they increased the network's stability
when deleted. There were two exceptions, Pagetopsis macropterus
(demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod),
that when deleted decreased the stability. Overall, 15 out of 490
species (3.06\%) gave rise to significant changes in the food web's
stability (Table 2).

After exploring the stability difference against the species properties
(Figure 5), we found that those species that generated a significant
impact on the stability of the food web are characterized by: 1) high
mean interaction strength; 2) mid to high trophic levels (TL
\textgreater{} 3.2); 3) relatively high number of interactions (Degree
\textgreater{} 25); and 4) mid to low trophic similarity values (TS
\textless{} 0.16). Habitat wise, species with a significant impact on
the stability are in all habitats, except for the benthic realm. Table 2
shows the results for such species.

@@

\begin{figure}
\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat. Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C). Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat. Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value). References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
\begin{tabular}{l c c c c c c c}
\tophline
